\section{Signal (ISO) and control background (1OS, 2OS, DD) skims}
\label{ref:sel:skims}

The signal and control skims are selected by inspecting if there exists
additional charged tracks that are compatible with coming from the
reconstructed \B vertex.
To predict the possibility of a charged track originating from the \B vertex,
a multivariate BDT, referred as ``isolation BDT'', is used.
The BDT is conceptually identical to the one used in
\cite{LHCb-ANA-2020-056} but with the BDT re-trained based on LHCb run 2
simulation.

The isolation BDT\footnote{
    The isolation BDT can be found at
    \techurllink{https://github.com/umd-lhcb/TupleToolSemiLeptonic/blob/master/Phys/TupleToolSemiLeptonic/src/TupleToolApplyIsolation.cpp}{github/umd-lhcb/TupleToolSemiLeptonic}.
} is added to the \davinci reconstruction sequence.
It loops over all charged tracks in the event\footnote{
    More specifically, these tracks are coming from
    \texttt{StdAllNoPIDsPions}, \texttt{StdNoPIDsUpPions},
    and \texttt{StdNoPIDsVeloPions}.
},
providing isolation scores for each of them where
higher score implies higher probability of coming from the vertex, named as
``anti-isolated''.
Three tracks with highest isolation scores\footnote{
    The ones that are most likely to be anti-isolated.
} are saved in the output file, in descending order\footnote{
    So the first one is the most anti-isolated one among all charged tracks
    in the event.
}.

Below a brief description for the signal sample and the main physics background
control samples is provided.
The actual isolation selections are listed in \cref{tab:skim-cut}.

\begin{itemize}
    \item ISO: $B \rightarrow D^{(*)} \lepton \neulb$, with $\lepton \in \{\muon,
        \tauon\}$.
        This is referred as signal, or ``isolated'', sample.
        It requires that no additional charged track is from the \B vertex
        (in a probabilistic sense, with probability related to the isolation
        score)
        and is compatible with a fully reconstructed \B decay
        (ignoring missing neutrino(s)).

    \item DD: $B \rightarrow D^{(*)}D X$,
        with dominate $D \rightarrow \Kp \mun \neumb X$ sub-decays.
        This is a double-charm ($DD$) control sample,
        which is selected by requiring at least one anti-isolated track,
        a \kaon-like long track\footnote{
            This means the track went through both upstream and downstream
            trackers, and is generally of good tracking quality.
        } and a hard track in the three most anti-isolated tracks\footnote{
            Note that these three requirements can be satisfied by a single
            track.
        }.

    \item 1OS: $B \rightarrow D^{**} \lepton \neulb$.
        This control sample, enriched in excited charm states,
        requires one and only one additional anti-isolated charged long track
        that is compatible with a \pion PID hypothesis and has correct charge
        for a $D^{**} \rightarrow D^{(*+)}\pim$ decay.

    \item 2OS: $B \rightarrow D^{**}_H \lepton \neulb$,
        where $H$ stands for ``heavy''.
        This control sample is enriched in highly excited (heavy) charm states,
        which is selected by requiring two and only two anti-isolated \pion-like
        long tracks of opposite charge,
        capable of $D^{**}_H \rightarrow D^{(*)} \pip\pim$ decay.

        % Why?
        This sample also provides an independent selection of
        $B \rightarrow D^{(*)}D X$ backgrounds, where the \pip\pim fit into the
        $X$ category and \kaon escapes isolation detection.
\end{itemize}

\begin{table}[htb]
    \caption{Signal and control sample isolation requirements.}
    \label{tab:skim-cut}
    \centering
    \begin{tabular}{c|rll}
        \toprule
        {\bf Sample}  & {\bf Variable}              & {\bf Cuts}     \\
        \midrule
        ISO           & \isoBDT{1}                  & $< 0.15$       \\
        \midrule
        1OS           & \isoBDT{1}                  & $> 0.15$       \\
                      & \isoBDT{2}                  & $< 0.15$       \\
                      & \isoTrack{1}                & $= 3$\parnote{
                          This means a long track.
                      }                                              \\
                      & $p_1$                       & $> 5$ GeV      \\
                      & $p_{T,1}$                   & $> 0.15$ GeV   \\
                      & \ProbNN{$K_1$}              & $< 0.2$        \\
                      & $Q_1 \cdot \text{PID}_\Dz$\parnote{
                          Apply to \Dz channel,
                          which implies that the anti-isolated \pip can
                          form a \Dstarp with the \Dz.
                      }                             & $> 0$          \\
                      & $Q_1 \cdot \text{PID}_\Dstar$\parnote{
                          Apply to \Dstar channel.
                          Here it is required that the anti-isolated \pim can
                          form a $D^{**0}$ with the \Dstarp.
                      }                             & $< 0$          \\
        \midrule
        2OS           & \isoBDT{1}                  & $> 0.15$       \\
                      & \isoBDT{2}                  & $> 0.15$       \\
                      & \isoBDT{3}                  & $< 0.15$       \\
                      & \isoTrack{1}                & $= 3$          \\
                      & \isoTrack{2}                & $= 3$          \\
                      & {\footnotesize
                         Max$(p_1 \cdot (p_{T,1} > 0.15 \text{ GeV}),
                              p_2 \cdot (p_{T,2} > 0.15 \text{ GeV}))$
                        }
                                                    & $> 5$ GeV      \\
                      & \ProbNN{$K_1$}              & $< 0.2$        \\
                      & \ProbNN{$K_2$}              & $< 0.2$        \\
                      & $Q_1 \cdot Q_2$             & $< 0$          \\
        \midrule
        DD            & \isoBDT{1}                  & $> 0.15$       \\
                      & {\footnotesize$\begin{aligned}
                            \text{Max}(
                            &p_1 \cdot (p_{T,1} > 0.15\text{ GeV}),  \\
                            &p_2 \cdot (p_{T,2} > 0.15\text{ GeV})
                                 \cdot (\text{\isoBDT{2}} > -1.1),   \\
                            &p_3 \cdot (p_{T,3} > 0.15\text{ GeV})
                                 \cdot (\text{\isoBDT{3}} > -1.1)
                            )
                        \end{aligned}$}             & $> 5$ GeV      \\
                      & Max(\ProbNN{$K_{1,2,3}$})   & $> 0.2$        \\
                      & \isoTrack{\text{the one passing $K$ PID requirement}}
                                                    & $= 3$          \\
                      & \isoBDT{\text{the one passing $K$ PID requirement}}
                                                    & $> -1.1$       \\
        \bottomrule
    \end{tabular}
    \begin{flushleft}
        \parnotes
    \end{flushleft}
\end{table}
